---
title: ""
output: 
  revealjs::revealjs_presentation:
    theme: moon
    mathjax: local
    includes:
    self_contained: false
    reveal_plugins: ["notes", "menu"]
    reveal_options:
      slideNumber: true
      progress: true
      history: true
      overview: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(png)
library(grid)
```

## Red Tomato Cost Analysis


```{r}
img1 <- readPNG("../images/redtomato.png")
 grid.raster(img1)
```

## Questions

* Are farmers making more for eco products?
* Are customers paying more for eco products?
* What percentage of items that get sold as eco to retailers get sold to consumers (regular people doing grocery shopping) as such?
* How do these numbers compare to national prices (based on terminal data)?

## Data cleaning

* The data that we investigated were Red Tomato’s purchase history and sales history 2014-2018.
* Purchase history: includes every order that every customer placed of every type of each species of produce, and how much it cost the customer to pay the farmers and the fees 
* Sales history
    * includes aggregate data on Red Tomato profits by every type of each species of produce 
* Final cleaned data
    * Apple species, ECOApple status, ECOApple visibility, Customer cost of farmer, Customer cost to logistics, Customer to RT, Total customer price
* Data checks for quality assurance between Sales and Purchase data


## Demos: 
* shiny app
* more robust d3 web app

```{r}
img2 <- readPNG("../images/RT_webapp.png")
 grid.raster(img2)
```


## Final thoughts

* what we delivered:
    * R package to process data
    * shiny app
    * d3 web app
* next steps:
    * make a package
    * finish the (more robust) web app
* repository (fork): https://github.com/cdelannoy/sourcingboston 
