---
title: ""
output: 
  revealjs::revealjs_presentation:
    theme: moon
    mathjax: local
    includes:
    self_contained: false
    reveal_plugins: ["notes", "menu"]
    reveal_options:
      slideNumber: true
      progress: true
      history: true
      overview: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(png)
library(grid)
```

## Red Tomato Cost Analysis


```{r}
img1 <- readPNG("../images/redtomato.png")
 grid.raster(img1)
```

## Questions

* Are farmers making more for eco products?
* Are customers paying more for eco products?
* What percentage of items that get sold as eco to retailers get sold to consumers (regular people doing grocery shopping) as such?
* How do these numbers compare to national prices (based on terminal data)?

## Data cleaning

## Demos: 
* shiny app
* more robust d3 web app

```{r}
img2 <- readPNG("../images/RT_webapp.png")
 grid.raster(img2)
```


## Final thoughts

* next steps:
    * make a package
    * finish the (more robust) web app
* repository (fork): https://github.com/cdelannoy/sourcingboston 
